Sketching for Density Estimation

### 2018-12-08 density.tex
komlos density

According to these notes \el{https://courses.cs.washington.edu/courses/cse522/11wi/scribes/lecture6.pdf find better ref} all
linear classifiers have Rademacher complexity $O(1/\sqrt{m})$. 
If we look at the proof in the last page, it is clear we can get also $K_m = \sqrt{d}/m$ which is better whenever $m>d$ which is pretty much always the case for linear classification (number of examples greater than $d$)

>>>>

According to these notes \el{https://courses.cs.washington.edu/courses/cse522/11wi/scribes/lecture6.pdf find better ref} all
linear classifiers have Rademacher complexity $O(1/\sqrt{m})$. 
If we look at the proof in the last page, it is clear we can get also $K_m = \sqrt{d}/m$ which is better whenever $m>d$ which is pretty much always the case for linear classification (number of examples greater than $d$) \el{I've done this in my head so it might not be right...}
